Visualizing Independence Using Extended Association Plots

### 2003-07-08 trunk/vcd/paper/dsc2003.Rnw
made changes necessary for the package, vignette and papers to pass R CMD check; vignette should probably be removed for release
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@273 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\documentclass[10pt]{article}
\usepackage{dsc2003}
\usepackage{Sweave, graphicx}
\usepackage{Z}

@@

\setkeys{Gin}{width=0.7\textwidth}
\begin{figure}[htbp]
\begin{center}
<<assoc-improved1,fig=TRUE,echo=FALSE,height=6,width=7,results=hide>>=
grid.assocplot(HairEyeColor[,,2], gp = gp.shading)
@
\caption{Extended association plot for `Hair' and `Eye' colors of female students.}
\label{fig:assoc-improved1}
\end{center}
\end{figure}
\pagebreak
\section{Improved visualization through residual shading}

@@

\setkeys{Gin}{width=0.7\textwidth}
\begin{figure}[htbp]
\begin{center}
<<assoc-improved,fig=TRUE,echo=FALSE,height=6,width=7,results=hide>>=
grid.assocplot(t(margin.table(HairEyeColor, c(1,3))), gp = gp.shading)
@
\caption{Extended association plot for `Hair' and `Sex' in the `HairEyeColor' data.}
\label{fig:assoc-improved2}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<UCB-mosaic-signif,fig=TRUE,echo=FALSE,height=8,width=8>>=
 panel.assocplot <- function (x, i, j, ..., axes, abbreviate) grid.assocplot(margin.table(x, c(i,j)), ..., panel = T, axis.labels = F, labels = F, main = NULL) 
grid.mosaicpairs(aperm(HairEyeColor), panel.upper= panel.assocplot, panel.lower = panel.assocplot, gp = gp.shading, main = NULL)
@
\caption{Extended association pairs for the `HairEyeColor' data,
  visualizing all pairwise marginal associations.}
\label{fig:HEC-pairs}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<UCB-assoc-signif,fig=TRUE,echo=FALSE,height=10,width=10>>=
tabplot(UCBAdmissions, gp = gp.shading)
@
\caption{Extended conditioning association plots for the `UCB Admissions' data.}
\label{fig:UCB-assoc-signif}
\end{center}
\end{figure}

>>>>

\documentclass[10pt]{article}
\usepackage{dsc2003}
\usepackage{Z}

@@

\setkeys{Gin}{width=0.7\textwidth}
\begin{figure}[htbp]
\begin{center}
<<assoc-improved1,fig=TRUE,echo=FALSE,height=6,width=7,results=hide>>=
grid.assocplot(HairEyeColor[,,2], gp = gp.Friendly)
@
\caption{Extended association plot for `Hair' and `Eye' colors of female students.}
\label{fig:assoc-improved1}
\end{center}
\end{figure}
\pagebreak
\section{Improved visualization through residual shading}

@@

\setkeys{Gin}{width=0.7\textwidth}
\begin{figure}[htbp]
\begin{center}
<<assoc-improved,fig=TRUE,echo=FALSE,height=6,width=7,results=hide>>=
grid.assocplot(t(margin.table(HairEyeColor, c(1,3))), gp = gp.Friendly)
@
\caption{Extended association plot for `Hair' and `Sex' in the `HairEyeColor' data.}
\label{fig:assoc-improved2}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<UCB-mosaic-signif,fig=TRUE,echo=FALSE,height=8,width=8>>=
 panel.assocplot <- function (x, i, j, ..., axes, abbreviate) grid.assocplot(margin.table(x, c(i,j)), ..., panel = T, axis.labels = F, labels = F, main = NULL)
grid.mosaicpairs(aperm(HairEyeColor), panel.upper= panel.assocplot, panel.lower = panel.assocplot, gp = gp.Friendly, main = NULL)
@
\caption{Extended association pairs for the `HairEyeColor' data,
  visualizing all pairwise marginal associations.}
\label{fig:HEC-pairs}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<UCB-assoc-signif,fig=TRUE,echo=FALSE,height=10,width=10>>=
tabplot(UCBAdmissions, gp = gp.Friendly)
@
\caption{Extended conditioning association plots for the `UCB Admissions' data.}
\label{fig:UCB-assoc-signif}
\end{center}
\end{figure}
